---
title: "Test of models"
author: "Ye Dam Yi"
date: "4/8/2021"
output: html_document
---


### Test of the models

#### Libraries
```{r libraries}
require(lavaan)
library(tidyverse)
library(haven)

```
#### Load data
```{r load-data}
risk_excluded <- read_sav("data/risk_excluded.sav")

# convert types
risk_excluded <- risk_excluded %>% 
  mutate_if(is.labelled, labelled::to_factor)


# reorder condition levels
risk_excluded <- risk_excluded %>% 
  mutate(condition = fct_relevel(condition, "Self", "Surrogate", "Prediction"),
         condition = fct_drop(condition, only = ""))

```

#### Check for normality
```{r normality}
# fit a model
risk_lm = lm(risklevel ~ 0 + condition, data = risk_excluded)

# create a data with two columns: condition and residuals
fits = risk_excluded %>%
    group_by(condition) %>%
    transmute(fit = mean(risklevel),
           residual = risklevel - mean(risklevel))

# look at homoscedasticity
fits %>% 
  ggplot(aes(x = condition, y = residual)) +
  geom_boxplot()

# look at normality of the residuals by condition
fits %>% 
  ggplot(aes(sample = residual)) +
  stat_qq() + facet_wrap(~ condition, ncol = 3)
  
# get the sd of the model
sd(risk_lm$residual)
round(summary(risk_lm)$sigma, 2)

# look at how the residuals compare to the fitted model of residuals
fits %>% 
  ggplot(aes(sample = residual)) +
  stat_qq() + geom_abline(intercept = mean(fits$residual), slope = summary(risk_lm)$sigma)


```
#### Coding for lavaan
##### Approach 1 - dummy coding
```{r dummy-coding, eval = FALSE}

# recode condition into two different conditions: 
# 1. self vs. surrogate decisions & 2. self decisions vs. predictions
# THe approach below didn't work with the error "x must be a `factor` object, not a logical vector." There seem to be no factor equivalent for NA
# risk_final <- risk_excluded %>%
#   mutate(recipient_sur = case_when(
#     condition == "Self" ~ condition,
#     condition == "Surrogate" ~ condition,
#     condition == "Prediction" ~ NA
#   ),
#     recipient_pred == case_when(
#       condition == "Self" ~ condition,
#       condition == "Surrogate" ~ NA,
#       condition == "Prediction" ~ condition
#     ))


# check factor levels
# levels(risk_excluded$condition)
glimpse(risk_excluded)

  # risk_final <- risk_excluded %>% 
  # mutate(recipient_sur = fct_recode(condition, NULL = "Prediction"),
  #        recipient_pred = fct_recode(condition, NULL = "Surrogate"))

risk_final <- risk_excluded %>% 
  mutate(condition_sur = case_when(
    condition == "Surrogate" ~ "1",
    TRUE ~ "0"),
    condition_pred = case_when(
      condition == "Prediction" ~ "1",
      TRUE ~ "0")) %>% 
  mutate(condition_sur = as.numeric(condition_sur),
         condition_pred = as.numeric(condition_pred))

```

I'm not really sure about this approach because if I used the dummy-coded condition_sur or condition_pred in my analysis, the observations belonging to prediction will be included in my analysis of self vs. surrogate conditions and vice versa. So I'm going to subset datasets into two.

##### Approach 2 - subsetting datasets
```{r subset-dataset}
# subset self & surrogate
risk_sur <- risk_excluded %>% 
  filter(condition == "Self" | condition == "Surrogate") %>% 
  mutate(condition = fct_drop(condition, only = "Prediction")) # drop irrelevant level
levels(risk_sur$condition)

# subset self & prediction
risk_pred <- risk_excluded %>% 
  filter(condition == "Self" | condition == "Prediction") %>% 
  mutate(condition = fct_drop(condition, only = "Surrogate")) # drop irrelevant level
levels(risk_pred$condition)

# the resulting data have three levels of condition
# drop the level that doesn't belong to each subsetted dataset

```


#### Self vs. surrogate decisions
##### Approach 1

```{r self-surrogate-mediation-dummy, eval = FALSE}

# total effect of recipient on y not controlling for m
self_sur_mediation <- '
    # direct effect
    risklevel ~ b1 * neg + b2 * pos + b3 * alert + c * condition_sur
    # mediator
    neg ~ a1 * condition_sur
    pos ~ a2 * condition_sur
    alert ~ a3 * condition_sur
    # indirect effect (a*b)
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    Indirect3 := a3 * b3
    # total effect
    total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
    # covariances
    neg ~~ pos
    pos ~~ alert
    neg ~~ alert
'
self_sur_fit <- sem(model = self_sur_mediation, data = risk_final, se = "bootstrap", bootstrap = 5000)
summary(self_sur_fit, fit.measures = TRUE, standardize = TRUE, estimates = TRUE)

mi <- modindices(self_sur_fit)
fitmeasures(self_sur_fit)

```


The nlminb command is intended for functions that have at least two continuous derivatives on all of the feasible region, including the boundary. For best results, the gradient of the objective should be supplied whenever possible. Supplying the Hessian matrix as well will sometimes, but not always, lead to a substantial decrease in the number of iterations required to reach a minimum.



##### Approach 2
```{r r self-surrogate-mediation-subset, eval = FALSE}

self_sur_mediation <- '
    # direct effect
    risklevel ~ b1 * neg + b2 * pos + b3 * alert + c * condition
    # mediator
    neg ~ a1 * condition_sur
    pos ~ a2 * condition_sur
    alert ~ a3 * condition_sur
    # indirect effect (a*b)
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    Indirect3 := a3 * b3
    # total effect
    total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
    # covariances
    neg ~~ pos
    pos ~~ alert
    neg ~~ alert
'
self_sur_fit <- sem(model = self_sur_mediation, data = risk_final, se = "bootstrap", bootstrap = 5000)
summary(self_sur_fit, fit.measures = TRUE, standardize = TRUE, estimates = TRUE)



```

```{r self-surrogate-moderation}

```

#### Self decisions vs. predictions
```{r self-prediction-mediation,eval = FALSE}
# total effect of recipient on y not controlling for m
self_pred_mediation <- '
    # direct effect
    risklevel ~ b1 * neg + b2 * pos + b3 * alert + c * condition_pred
    # mediator
    neg ~ a1 * condition_pred
    pos ~ a2 * condition_pred
    alert ~ a3 * condition_pred
    # indirect effect (a*b)
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    Indirect3 := a3 * b3
    # total effect
    total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
    # covariances
    neg ~~ pos
    pos ~~ alert
    neg ~~ alert
'
self_pred_fit <- sem(model = self_pred_mediation, data = risk_final, se = "bootstrap", bootstrap = 5000)
summary(self_pred_fit, fit.measures = TRUE, standardize = TRUE, estimates = TRUE)

mi <- modindices(self_pred_fit)
fitmeasures(self_pred_fit)

```

```{r self-prediction-moderation}

```




```


