---
title: "Analysis"
author: "Ye Dam Yi"
date: "4/6/2021"
output: html_document
---

#### Load data
```{r setup, include=FALSE}
library(tidyverse)
library(labelled)
library(rstatix)
library(haven)
library(knitr)

```

```{r load-data}
risk <- read_spss("data/risk_clean.sav")
```


#### Exclusion
```{r exclusion}
# check data
glimpse(risk)

# convert types
# risk <- risk %>% 
#   mutate(gender = as_factor(gender),
#          condition = as_factor(condition),
#          rel_self = as.numeric(as_factor(rel_self)),
#          rel_friend1 = as.numeric(as_factor(rel_friend1)),
#          rel_friend2 = as_factor(rel_friend2))

# check data
# glimpse(risk)

# get participant info from the raw data
# gender
risk %>% 
  group_by(gender) %>% 
  count() %>% 
  group_by() %>% 
  mutate(percent = n/sum(n))

# age
risk %>% 
  filter(age < 1000) %>% 
  summarise(mean = mean(age,na.rm = TRUE), 
            sd = sd(age,na.rm = TRUE),
            min = min(age,na.rm = TRUE),
            max = max(age,na.rm = TRUE)
            )


# exclude those who failed at attention checks and who didn't consent to participate
risk_excluded <- risk %>% 
  filter(attention1 == 7 & attention2 == 3 & consent == 1) %>% 
# exclude those who indicated their gender to be non-binary or other/prefer not to say
  filter(gender == 1 | gender ==2) 

# check file
glimpse(risk_excluded)
# write file
write_sav(risk_excluded, "data/risk_excluded.sav")

```


There is one non-consent. This observation needs to be excluded. 

After excluding those who didn't consent to participate and those who failed at either of the two attention check questions, there were 579 participants remaining to be part of analysis.

After excluding those who indicated their gender to be non-binary or other/prefer not to say, there were 569 participants remaining. 



### Who are my participants?
```{r participant-viz}
# gender
risk_excluded %>% 
  ggplot(aes(x = gender)) +
  geom_bar() +
  labs()

# condition by gender and by relationship status for self and for friend 1
risk_excluded %>% 
  ggplot(aes(y = condition, fill = gender)) +
  geom_bar() +
  facet_wrap(vars(rel_self, rel_friend1), labeller = "label_both")

# relationship status - self
risk_excluded %>% 
  ggplot(aes(y = rel_self, fill = gender)) +
  geom_bar()

# relationship status - friend 1
risk_excluded %>% 
  ggplot(aes(y = rel_friend1, fill = gender)) +
  geom_bar()


# numerical variables
# age
risk_excluded %>% 
  ggplot(aes(y = age, color = condition)) +
  geom_boxplot()

# set anomaly to na
risk_excluded <- risk_excluded %>% 
  mutate(age = case_when(
    age >= 1000 ~ NA_real_, # NA_real_ is the double type counterpart to NA
    TRUE ~ age
  ),
  .keep = "unused")

# check again
risk_excluded %>% 
  ggplot(aes(y = age, color = condition)) +
  geom_boxplot()

# time
risk_excluded %>% 
  ggplot(aes(y = time)) +
  geom_boxplot()

```

```{r participant-num}
# count by variables
# overall
risk_excluded %>% 
  group_by(gender, condition, rel_self, rel_friend1, rel_friend2) %>% 
  count() %>% 
  group_by() %>% 
  mutate(percent = n/sum(n))

# gender
risk_excluded %>% 
  group_by(gender) %>% 
  count() %>% 
  group_by() %>% 
  mutate(percent = n/sum(n))

# condition
risk_excluded %>% 
  group_by(condition) %>% 
  count() %>% 
  group_by() %>% 
  mutate(percent = n/sum(n))

# self relationship status
risk_excluded %>% 
  group_by(rel_self) %>% 
  count() %>% 
  group_by() %>% 
  mutate(percent = n/sum(n))

# friend 1 relationship status
risk_excluded %>% 
  group_by(rel_friend1) %>% 
  count() %>% 
  group_by() %>% 
  mutate(percent = n/sum(n))

## function - didn't work
# prop <-  function(data = risk_excluded, var) {
#  data %>% 
#  group_by(var) %>% 
#  count() %>% 
#  group_by() %>% 
#  mutate(percent = n/sum(n))
#}
# prop(risk_excluded$condition)


# numerical variables
# age
risk_excluded %>% 
  group_by(gender) %>% 
  summarise(mean = mean(age,na.rm = TRUE), 
            sd = sd(age,na.rm = TRUE),
            min = min(age,na.rm = TRUE),
            max = max(age,na.rm = TRUE))

# inspect why there's NA for female age
risk_excluded %>% 
  filter(gender == 2)
# revised the code above to remove missing values

# time
risk_excluded %>% 
  group_by(gender) %>% 
  summarise(mean = mean(time,na.rm = TRUE), 
            sd = sd(time,na.rm = TRUE),
            min = min(time,na.rm = TRUE),
            max = max(time,na.rm = TRUE)
            )

```


#### Use rstatix to get summary data
```{r summary}
# categorical variables
risk_excluded %>% 
  freq_table(gender, condition, rel_self, rel_friend1, rel_friend2)

# numerical variables
risk_excluded %>% 
  filter(age < 1000) %>% 
  get_summary_stats(age, time)

# identify outliers
risk_excluded %>% 
  identify_outliers(age)
risk_excluded %>% 
  identify_outliers(time)
```





#### Manipulation check
```{r manipulation-check}
# visualize
risk_excluded %>% 
  pivot_longer(c(riskyrisk, riskavrisk), names_to = "option", values_to = "riskrating") %>% 
  ggplot(aes(x = option, y = riskrating)) +
  geom_boxplot() +
  scale_x_discrete(labels = c("Risk-Averse Option", "Risky Option")) +
  theme_bw()

# look at the numbers
risk_excluded %>% 
  get_summary_stats(riskyrisk, riskavrisk, type = "mean_sd")


# compare means
t.test(risk_excluded$riskyrisk, risk_excluded$riskavrisk, paired = TRUE) %>% 
  tidy() # %>% 
  # kable()


```

People rated the risky option to be significantly higher than the risk-averse option. 




