---
title: "Cleanup"
author: "Ye Dam Yi"
date: "4/5/2021"
output: html_document
---

#### Libraries
```{r setup, include=FALSE}
library(tidyverse)
library(haven)
```


#### Read in data
```{r read-data}
riskraw <- haven::read_spss("data/relationship_raw.sav")
riskraw <- riskraw %>% 
  rename_with(tolower) %>% 
  select(duration__in_seconds_, consent:fl_40_do_maleprediction)

write_sav(riskraw, "data/relationship.sav")
```


#### Recode rel_self
```{r recode-incorrect-values, include=FALSE, eval= FALSE}
# make sure that all the rel-self values are coded correctly
# bring in choice text data
choicetext <- read_csv("/Users/yedam/Documents/Academic/WFU/Psychology/Projects/Thesis/Data/Raw data/choice_text.csv")
head(choicetext)

rel_self <- as_tibble(choicetext$rel_self)
rel_self <- rel_self %>% 
  mutate(id = 1:615)

# delete first 2 rows
rel_self <- rel_self[ !(rel_self$id) %in% c(1,2), ]
relselfchoice <- rel_self %>%
  select(value) %>% 
  mutate(id = 1:613)

# save output
write_sav(relselfchoice, "data/relself.sav")

# create id in risk
riskraw <- riskraw %>% 
  mutate(id = 1:613)

# bind rel_self and risk
riskraw <- merge(relselfchoice, risk)


# check coding 
riskraw %>% 
  relocate(rel_self, .after = value) # output shows that there's no need to recode rel_self

# drop value
riskraw <- riskraw %>% 
  select(-value)


```


I inspected the data again and saw that all the values in the rel_self column were correctly coded to begin with. So there was no need for this code chunk. 


#### Restructure data
```{r glimpase-data, eval = FALSE}
# attempts that didn't work
# collapse risk, pos, neg, and alert columns across conditions    
# risk <- risk %>% 
#    pivot_longer(
#      cols = ends_with(c("_risk", "_pos", "_neg", "_alert")),
#      names_pattern = "(.+)_(.+)",
#      names_to = c("conditiontext",".value"),
#    ) %>% 
# collapse condition columns
#risk %>%     
#  pivot_longer(
#      cols = starts_with(c("fl_30_do_", "fl_40_do_")),
#      names_pattern = "(.+)_(.+)_(.+)_(.+)",
#      names_to = c(NA, NA, ".value", "condition")
#    ) %>% 
# drop condition variables
#    select(!starts_with("fl_"))


# collapse condition variables
# 1. rename condition variables & drop used variables & put time after consent
head(riskraw)
riskraw <- riskraw %>% 
  mutate(femself_condition = fl_30_do_femaleselfdecision,
         femsur_condition = fl_30_do_femalesurrogatedecision,
         fempred_condition = fl_30_do_femaleprediction,
         malself_condition = fl_40_do_maleselfdecision,
         malsur_condition = fl_40_do_malesurrogatedecision,
         malpred_condition = fl_40_do_maleprediction,
         time = duration__in_seconds_,
         .keep = "unused"
  ) %>% 
  relocate(time, .after = consent)

# 2. create condition variable
riskraw <- riskraw %>% 
  mutate(gendcond = case_when(
                              femself_condition == 1 ~ "femself",
                              femsur_condition == 1 ~ "femsur",
                              fempred_condition == 1 ~ "fempred",
                              malself_condition == 1 ~ "malself",
                              malsur_condition == 1 ~"malsur",
                              malpred_condition == 1 ~"malpred"),
         .keep = "unused"
                              
  )

# 3. recode ratings by condition
# risk levels
riskraw <- riskraw %>% 
  mutate(risklevel = case_when(
    gendcond == "femself" ~ femsel_risk,
    gendcond == "femsur" ~ femsur_risk,
    gendcond == "fempred" ~ fempred_risk,
    gendcond == "malself" ~ malsel_risk,
    gendcond == "malsur" ~ malsur_risk,
    gendcond == "malpred" ~ malpred_risk
  ),
  # positive emotion
  pos = case_when(
    gendcond == "femself" ~ femsel_pos,
    gendcond == "femsur" ~ femsur_pos,
    gendcond == "fempred" ~ fempred_pos,
    gendcond == "malself" ~ malsel_pos,
    gendcond == "malsur" ~ malsur_pos,
    gendcond == "malpred" ~ malpred_pos
  ),
  # negative emotion
  neg = case_when(
    gendcond == "femself" ~ femsel_neg,
    gendcond == "femsur" ~ femsur_neg,
    gendcond == "fempred" ~ fempred_neg,
    gendcond == "malself" ~ malsel_neg,
    gendcond == "malsur" ~ malsur_neg,
    gendcond == "malpred" ~ malpred_neg
  ),
  # alertness ratings
 alert = case_when(
    gendcond == "femself" ~ femsel_alert,
    gendcond == "femsur" ~ femsur_alert,
    gendcond == "fempred" ~ fempred_alert,
    gendcond == "malself" ~ malsel_alert,
    gendcond == "malsur" ~ malsur_alert,
    gendcond == "malpred" ~ malpred_alert
  ))

# 4. create combined condition variable
riskraw <- riskraw %>% 
  mutate(condition = case_when(
    gendcond == "femself" | gendcond == "malself" ~ "Self",
    gendcond == "femsur" | gendcond == "malsur" ~ "Surrogate",
    gendcond == "fempred" | gendcond ==  "malpred" ~ "Prediction"
  ))

# 5. select columns I'm interested in
riskraw <- riskraw %>% 
  select(consent:gender, gendcond, condition, friend1, friend2, risklevel:alert, riskyrisk:code)

# write_csv(risk, file = "data/risk.csv")

```


I'm not exactly sure if my approach is the most optimal. 


#### Compare Qualtrics and Amazon MTurk codes

```{r compare-code}
# read in data
batch1 <- read_csv("/Users/yedam/Documents/Academic/WFU/Psychology/Projects/Thesis/Data/Batches/batch1_27.csv", na = c("", "NA"))
batch2 <- read_csv("/Users/yedam/Documents/Academic/WFU/Psychology/Projects/Thesis/Data/Batches/batch2_27.csv", na = c("", "NA"))
batch3 <- read_csv("/Users/yedam/Documents/Academic/WFU/Psychology/Projects/Thesis/Data/Batches/batch3_549.csv", na = c("", "NA"))

# convert names into lowercase - extract worker id
extractcode <- function(df){
  rename_with(df, tolower) %>% 
     select(answer.surveycode)
}

# extract codes
code1 <- extractcode(batch1)
code2 <- extractcode(batch2)
code3 <- extractcode(batch3)

# combine into 1
code <- bind_rows(code1, code2, code3)

# write file
write_csv(code, file = "data/code.csv")

```


I compared the survey code in each of the risk and code files to make sure that they were consistent with each other. There were several NA's in the Mturk file, which makes sense. 


```{r select-rows}
# select rows in risk that have the survey code in the code column in code
# 1. create key id variable
riskraw <- riskraw %>% 
  mutate(id = 1:nrow(riskraw))
code <- code %>% 
  mutate(id = 1:nrow(code)) %>% 
  rename(code_mturk = answer.surveycode)

# 2. merge two files
riskraw <- riskraw %>% 
  right_join(code)

# 3. select rows whose mturk code is NOT missing
riskraw <- riskraw %>% 
  filter(!is.na(code_mturk))

# 4. write file
write_sav(riskraw, "data/risk.sav")
```


