---
title: "Analysis"
author: "Ye Dam Yi"
date: "4/6/2021"
output: html_document
---

#### Load data
```{r setup, include=FALSE}
library(tidyverse)
library(labelled)
library(ggpubr)
library(rstatix)
library(psych)
library(haven)

```

```{r load-data}
risk <- read_sav("data/risk_nonlabelled.sav")
```


#### Exclusion
```{r exclusion}
# convert types
risk <- risk %>% 
  mutate_if(is.labelled, labelled::to_factor)

# exclude those who failed at attention checks and who didn't consent to participate
risk_excluded <- risk %>% 
  filter(attention1 == 7 & attention2 == 3 & consent == 1) %>% 
# exclude those who indicated their gender to be non-binary or other/prefer not to say
  filter(gender == 1 | gender ==2) 


```


There is one non-consent. This observation needs to be excluded. 

After excluding those who didn't consent to participate and those who failed at either of the two attention check questions, there were 579 participants remaining to be part of analysis.

After excluding those who indicated their gender to be non-binary or other/prefer not to say, there were 569 participants remaining. 



### Who are my participants?
```{r participant, eval = FALSE}
# gender
risk_excluded %>% 
  ggplot(aes(x = gender)) +
  geom_bar() +
  labs()

# condition by gender
risk_excluded %>% 
  ggplot(aes(y = condition, fill = gender)) +
  geom_bar()
```
